I mean really clean the pheno and get to know the hell of the samples

### 2019-11-03 scripts/01_clean_pheno.Rmd
update
clean the fucking toxicity grade var

@@

>>>>

```{r}
# the final pheno table which has 33 rows
final_pheno <- phe_M_clean %>% 
  filter(Sampleid %in% have_sg$sample_id)

final_pheno %>% 
  write_csv('../data/cleaned_pheno/final_pheno.csv')
```

@@

```{r}
# retrieve the toxicity grade info from the event table
events <- read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/CTC Event Table 10232019 wo Censor .xlsx',
                    sheet = 3) %>% 
  select(MRN, Event, `Event Description`, `Event Stop`) %>% 
  rename(descr = names(.)[3],
         stop = names(.)[4]) %>% 
  filter(Event %in% c('CRS','ICANS')) %>% 
  mutate(grade = if_else(str_detect(descr, '^No'), '0', str_extract(descr, '[1|2|3]'))) %>% 
  select(-descr)

table(events$Event)

# 35402481 patient ICANS record missing.

# try with the CRS first
tox_CRS <- events %>% 
  filter(Event == 'CRS')

table(tox_CRS$grade)

# try to get the sample id from MRN
# this part was manually done by me cleaning M's table

# below is for CRS only
samps <- read_csv('../data/cleaned_pheno/MRN_sampleid.txt', col_types = 'cc') %>% 
  left_join(tox_CRS, by  = 'MRN') %>% 
  filter(sampleid %in% pheno$Sampleid) %>% 
  # really mad that i have to remove some records in this way
  mutate(stop = replace(stop, MRN == '35546332' & grade == '0', '2018-01-30')) %>% 
  arrange(desc(stop)) %>% 
  distinct(sampleid, .keep_all = T)

# 35546332 has both None and grade 1 for CRS
# based on the date choose the 0
# choose the latest date grade for 00332772 : 1
# choose the latest date grade for 35546332 : 0
```
